---
title: "How it works"
author: "Cervan Girard"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How it works}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(eval=FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

# 1 -  Get the token

We have to get back our todoist token.

*2 options :*

## ask for an app dedicated token


Go to the [Manage app console](https://developer.todoist.com/appconsole.html) and create a new app. Give a name and click on create app. 

A page opens with the Client ID and the Secret Client to use for the get_token function. Add ()[http://localhost:1410] to the "OAuth redirect URL".

Now, get the token: 
```{r}
library(todoist)
token <- get_todoist_api_token()
```



Be careful, the function ask if you want to copy the result into an .httr-oauth file. If you agree, do not forget to put this file in the `.gitgnore` file.

## get the token from the todoist website
```{r}
library(todoist)
todoist::open_todoist_website_profile()
token <- "YOURTOKEN" # copied and pasted from website
```


## Now save your token securly into R (one time per computer)


```{r}
set_todoist_api_token(token)
```



# 2 - Now, let's play !

## Create new porject, add tasks and users

```{r}
add_project(project_name = "test",verbose = TRUE) %>%
  init_presta() %>%
  add_users_in_project(list_of_users = "your@mail.fr")
```

The functions return the project id. So we can do a series of actions.
