---
title: "How it works"
author: "Cervan Girard"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How it works}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  eval=FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

# 1 -  Get the token

The first step is to retrieve a token.

Open todoist website to find it :

```{r}
library(rtodoist)
rtodoist::open_todoist_website_profile()
token <- "YOURTOKEN" # copied and pasted from website
library(lubridate)
```


## Now save your token securly into R (one time per computer)

We use {keyring} features to do it. 

```{r}
set_todoist_api_token(token)
```


# 2 - Now, let's play !

## Create new project, add tasks and users

#### Add new project

Don't forget to store the result to reuse the identifier of the new project.

```{r}
id_proj <- add_project(project_name = "test",verbose = TRUE) 
```

#### Add task to this project

```{r}
id_proj %>%
  add_tasks_in_project("my_tasks")
```

#### Add users to this porject

```{r}
id_proj %>%
  add_users_in_project(list_of_users = "your@mail.fr")
```

#### All in the same time 

```{r}
add_project(project_name = "test",verbose = TRUE) %>%
  add_tasks_in_project(tasks_list = 
                         list("First task",
                              "Second task")
                       ) %>%
  add_responsible_to_task("First task", add_responsible = "jean@mail.fr")
```


#### More specific :



You can set  multiple task at ones, you can set muliple responsible due date and section
if you use vectors, the order is important. and the matching will be done term by term

**multiple** tasks for **one** responsible with **one** due dates

```{r}
id_proj %>% 
  add_tasks_in_project(tasks_list = c("t1","t2"),responsible = c("user1@mail.com"),due = today())
```

**multiple** tasks for **one** responsible with **multiple** due dates

```{r}

id_proj %>% 
  add_tasks_in_project(tasks_list = c("t1","t2"),responsible = c("user1@mail.com"),due = today() + days(1:2))
```

**multiple** tasks for **multiple** responsible with **on** due dates on many section

```{r}
id_proj %>% 
  add_tasks_in_project(tasks_list = c("t1","t2"),responsible = c("user1@mail.com","user2@mail.com"),due = lubridate::today(),section_name = c("S1","S2"))
```


you can pass a data.frame using `add_tasks_in_project_from_df`

```{r}

tasks_list_df <- data.frame(
  "tasks_list" = LETTERS[1:5],
  "responsible" = glue::glue("user{1:5}@mail.com"),
  "due" = today()+ days(1:5),
  "section_name" = c("S1","S1","S3","S3","S3")
  
)

add_tasks_in_project_from_df(project_id = id_proj,tasks_list_df = tasks_list_df)
```




